### 2015-05-15 whoop.tex
moved toolchain figure earlier
fix

@@

The simple concurrent programming model of \S\ref{sec:symbolicpairwise} is deliberately idealistic to make it easy to describe our symbolic verification technique. In practice, Linux drivers are written in C, we do not know up-front which are the entry points for a driver, drivers do not work with a cleanly specified set of named locks, and rather than having a given set of named shared variables, we have arbitrary memory accesses via pointers. We now explain how we have taken the conceptual ideas from \S\ref{sec:symbolicpairwise} and used them to build \whoop\footnote{\url{https://github.com/pdeligia/whoop}}, a practical, fully automatic tool for detecting data races in drivers.

\begin{figure*}
\centering
\includegraphics[width=.99\linewidth]{img/whoop.pdf}
\vspace{-2mm}
\caption{The \whoop architecture, empowered by state-of-the-art compilation (Clang/LLVM and SMACK) and verification (Boogie and \corral) tools}
\vspace{-2mm}
\label{fig:whoop}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=.99\linewidth]{img/whoop.pdf}
\vspace{-2mm}
\caption{The \whoop architecture, empowered by state-of-the-art compilation (Clang/LLVM and SMACK) and verification (Boogie and \corral) tools}
\vspace{-3mm}
\label{fig:whoop}
\end{figure*}

@@

The simple concurrent programming model of \S\ref{sec:symbolicpairwise} is deliberately idealistic to make it easy to describe our symbolic verification technique. In practice, Linux drivers are written in C, our technique does not know up-front which are the driver entry points, drivers do not work with a cleanly specified set of named locks, and rather than having a given set of named shared variables, we have arbitrary memory accesses via pointers. We now explain how we have taken the conceptual ideas from \S\ref{sec:symbolicpairwise} and used them to build \whoop\footnote{\url{https://github.com/pdeligia/whoop}}, a practical, fully automatic tool for detecting data races in drivers.
